Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2023-02-14 src/tex/ms.tex

We apply the method described in section \textbf{\ref{subsec:stats}} to the first GW event GW150914 \citep{GW150914}.
We use the \texttt{Overall\_posterior} posterior samples for GW150914,
publicly available from the Gravitational wave Open Science Center \citep{LIGOScientific:2019lzm}. 
The parameters involved in the analysis and the range we allow for the inference are tabulated in table \ref{tab:parameters}.
The spin of BHs formed in isolated binaries depends strongly on the angular
momentum transport in massive stars which is still highly uncertain (see however \citet{Fuller2019, Bavera2020}),
therefore we only consider the two component masses in the observable space $\bm{\theta}$ in both the
root-finding stage and the MCMC stage.

For progenitor parameters $\bm{\theta'}$, we characterize each guess with
five parameters: the two component masses $M_{\rm 1,ZAMS}$ and $M_{\rm 2,ZAMS}$, the orbital period $t_{\rm orb}$,
the eccentricity $e$, and the metallicity $Z$ at ZAMS. Note that the progenitor formation redshift is not
obtained through the root-finding process because the formation redshift does not intrinsically affect
the evolution of the binary. Instead, we compute the time it takes for the binary to evolve from
formation to the merger and add this time to the lookback time when a GW event is observed and limit the total
time to merger to be less than $13.7\,\rm{Gyr}$.
Using the total lookback time, we can compute the redshift of the binary at ZAMS formation following the
Planck 2018 cosmological model \citep{Planck2018}.
The main benefit of post-processing the redshift in this way is that we do not rely on a particular assumption
of star formation rate (SFR) distribution when we solve for the posterior distribution in redshift.
This means we can put the prior on formation redshift (or in general, metallicity-redshfit distribution) in
by reweighting the posterior distribution according to a particular SFR model,
and therefore do not have to rerun the inference every time we change the SFR model. This is especially helpful
since SFR models are still highly uncertain but strongly impact the local merger rates of BBHs \citep[e.g. ][]{Broekgaarden2021}.

For hyperparameters $\bm{\lambda}$, we choose parameters that strongly affect
binary evolution in \texttt{COSMIC} for massive stars, including the common envelope
efficiency $\alpha$, the fraction of mass accreted onto the accretor during stable mass transfer $f_{\rm acc}$,
the critical mass ratio which determines whether Roche-overflow mass transfer
proceeds stably or produces a common envelope when the donor star is on the Hertzsprung gap
$q_{\rm crit,3}$, and the root-mean-square of the Maxwellian distribution
employed for CO natal kicks, $\sigma$. 
%Prior

>>>>

We apply the method described in section \textbf{\ref{subsec:stats}} to the
first GW event GW150914 \citep{GW150914}. We use the \texttt{Overall\_posterior}
posterior samples for GW150914, publicly available from the Gravitational wave
Open Science Center \citep{LIGOScientific:2019lzm}. The parameters involved in
the analysis and the range we allow for the inference are tabulated in table
\ref{tab:parameters}. The spin of BHs formed in isolated binaries depends
strongly on the angular momentum transport in massive stars which is still
highly uncertain (see however \citet{Fuller2019, Bavera2020}), therefore we only
consider the two component masses in the observable space $\bm{\theta}$ in both
the root-finding stage and the MCMC stage. \textbf{Instead of the sampling the posterior
in the two component masses space, we choose to perform the KDE in the chirp
mass and mass ratio space, which are less degenerate and is less prone to error
from the KDE.}

For progenitor parameters $\bm{\theta'}$, we characterize each guess with five
parameters: the two component masses $M_{\rm 1,ZAMS}$ and $M_{\rm 2,ZAMS}$, the
orbital period $t_{\rm orb}$, the eccentricity $e$, and the metallicity $Z$ at
ZAMS. \textbf{We use a log-uniform prior in sampling $M_{\rm 1,ZAMS}$, $M_{\rm
2,ZAMS}$, $t_{\rm orb}$, and $Z$, and we use a uniform prior for $e$.
The range follows the range for the optimization range as given by table
\ref{tab:parameters}.} Note that the progenitor formation redshift is not
obtained through the root-finding process because the formation redshift does
not intrinsically affect the evolution of the binary. Instead, we compute the
time it takes for the binary to evolve from formation to the merger and add this
time to the lookback time when a GW event is observed and limit the total time
to merger to be less than $13.7\,\rm{Gyr}$. Using the total lookback time, we
can compute the redshift of the binary at ZAMS formation following the Planck
2018 cosmological model \citep{Planck2018}. The main benefit of post-processing
the redshift in this way is that we do not rely on a particular assumption of
star formation rate (SFR) distribution when we solve for the posterior
distribution in redshift. This means we can put the prior on formation redshift
(or in general, metallicity-redshfit distribution) in by reweighting the
posterior distribution according to a particular SFR model, and therefore do not
have to rerun the inference every time we change the SFR model. This is
especially helpful since SFR models are still highly uncertain but strongly
impact the local merger rates of BBHs \citep[e.g. ][]{Broekgaarden2021}.

For hyperparameters $\bm{\lambda}$, we choose parameters that strongly affect
binary evolution in \texttt{COSMIC} for massive stars, including the common
envelope efficiency $\alpha$, the fraction of mass accreted onto the accretor
during stable mass transfer $f_{\rm acc}$, the critical mass ratio which
determines whether Roche-overflow mass transfer proceeds stably or produces a
common envelope when the donor star is on the Hertzsprung gap $q_{\rm crit,3}$,
and the root-mean-square of the Maxwellian distribution employed for CO natal
kicks, $\sigma$. \textbf{We use a uniform prior for $\alpha$, $f_{\rm acc}$, and
$q_{\rm crit,3}$, and a log-uniform prior for $\sigma$.}

\textbf{We use the same prior for all the events in this study. Note that our
main goal is to see whether the events are compatible with \textsc{COSMIC} on an
individual event basis, we do not consider any population analysis here, and
therefore we do not account for any selection effect.}
